A Data-Driven Framework for Neural Field Modeling

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex

    \section{Reviewer 2}

    We thank the reviewer for their encouraging review. Each point raised is dealt with in turn.

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.

	\emph{To address this point, we have added an extra section to the discussion, `Modeling Assumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}
	\emph{\mike{We would like to directly address the idea of representing the error using an autoregressive model. The reason we have not performed this kind of extension in the paper is that we have attempted to remain as close as possible to the original Wilson and Cowan model, to show that such models can be inferred from data. Done properly, modelling the error as an autoregressive process  will introduce additional connectivity kernels, one for each temporal lag in the AR process, i.e.
	\begin{equation}
	   e_t(s) = \sum_i \int_\Omega K_i(s,s')e_{t-i}(s')ds'
	\end{equation} 
where $K_i$ is the $i^\mathrm{th}$ connectivity kernel. Hence this would imply something about the connectivity in the field that we would need to relate to an extension in the underlying field model or its discretisation. Having said this, we are considering various model extensions, and that of higher order temporal dynamics is particularly intriguing due to the additional richness of signal we can represent.}}

### 2011-01-11 ltx/first_order_framework/response_to_reviews.tex

\item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010. I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.

\dean{\emph{The authors do not have much to add to this comment. We feel that adding the disturbance to the firing rate is appropriate for this model, which is what we have done, and it agrees with the work by Benayoun et al PloS Comp Biol 2010. By the central limit theorem, we expect the disturbance to be Gaussian and due to the structural organization of the cortex, we expect the disturance to be spatially colored. In future work we plan to add to the framework and show how the disturbance properties can also be estimated from data.}}

### 2011-01-12 ltx/data_paper/DataPaper.tex
corrected observation noise covariance estimation in dara paper

\title{Patient-Specific Neural Field Modeling from Micro-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
 David B. Grayden and Visakan Kadirkamanathan  }

@@

2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \boldsymbol\Sigma_{\epsilon}- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\

@@

  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\

@@

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \boldsymbol\Sigma_{\epsilon}-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\

@@

When taking the derivative of equation~\ref{eq:Voldermont}, the constant $\beta$ described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
\begin{equation}\label{eq:Qpartialtheta}
 \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=2\Xi_0-\boldsymbol\theta^\top(\Xi_2^\top+\Xi_2)-2\xi\Xi_3
\end{equation}
noting that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
\begin{equation}\label{eq:theta}
 \boldsymbol \theta=\Xi_2^{-1}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
\end{equation}
similarly differentiating with respect to $\xi$ we have
\begin{equation}\label{eq:Qpartialxi}
 \frac{\partial \mathcal Q}{\partial \xi}=2tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace -2 \Xi_3 \boldsymbol\theta - 2\xi tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace
\end{equation}
substituting \ref{eq:theta} in \ref{eq:Qpartialxi} and equating to zero we get
\begin{equation}
 \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_3^\top}
\end{equation}
differentiating equation~\ref{eq:Voldermont} with respect to $\boldsymbol\Sigma_{\epsilon}$ we get
\begin{equation}
 \frac{\partial \mathcal Q}{\partial \boldsymbol\Sigma_{\epsilon}}= (T-1)\boldsymbol\Sigma_{\epsilon}-\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]=\mathbf 0
\end{equation}
therefore we have
\begin{equation}
 \boldsymbol\Sigma_{\epsilon}=\frac{1}{T-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right]
\end{equation}

>>>>

\title{Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
 David B. Grayden and Visakan Kadirkamanathan  }

@@

2\ln p(\mathbf x_{t+1} , \mathbf y_{t+1};\boldsymbol\Theta)&=&-\ln \mid\boldsymbol\Sigma_{\epsilon}\mid- (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})\nonumber \\

@@

  \ln p(\mathbf x_{t+1}, \mathbf y_{t+1};\boldsymbol\Theta)&=& -\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}(\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf  x_{t+1})^\top\right\rbrace   \nonumber \\

@@

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&\approx& -(T-1)\ln \mid\boldsymbol\Sigma_{\epsilon}\mid-\mathrm{tr}\left\lbrace\boldsymbol\Sigma_{\epsilon}^{-1}\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace\nonumber \\

@@

When taking the derivative of equation~\ref{eq:Voldermont}, the constant $\beta$ described in equation~\ref{eq:def of beta} will disappear. Differntiating with respect to $\boldsymbol\theta$ we have
\begin{equation}\label{eq:Qpartialtheta}
 \frac{\partial \mathcal Q}{\partial \boldsymbol\theta}=2\Xi_0-\boldsymbol\theta^\top(\Xi_2^\top+\Xi_2)-2\xi\Xi_3
\end{equation}
noting that $\Xi_2$ is symmetric and equating \ref{eq:Qpartialtheta} to the zero vector we get
\begin{equation}\label{eq:theta}
 \boldsymbol \theta=\Xi_2^{-1}\left(\Xi_0^\top-\xi\Xi_3^\top \right)
\end{equation}
similarly differentiating with respect to $\xi$ we have
\begin{equation}\label{eq:Qpartialxi}
 \frac{\partial \mathcal Q}{\partial \xi}=2tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace -2 \Xi_3 \boldsymbol\theta - 2\xi tr \left\lbrace\Xi_4\boldsymbol\Sigma_e^{-1} \right\rbrace
\end{equation}
substituting \ref{eq:theta} in \ref{eq:Qpartialxi} and equating to zero we get
\begin{equation}
 \xi=\frac{tr\left\lbrace \Xi_1 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_0^\top}{tr\left\lbrace \Xi_4 \boldsymbol\Sigma_e^{-1}\right\rbrace-\Xi_3\Xi_2^{-1}\Xi_3^\top}
\end{equation}
Rewrite equation~\ref{eq:Voldermont} as
\begin{equation}
 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')\propto-(T-1)n_y\ln\sigma^2_{\epsilon}-\frac{1}{\sigma_{\epsilon}^2}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
\end{equation}
differentiating with respect to $\sigma_{\epsilon}^2$
\begin{equation}
  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon^4}}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace
\end{equation}
setting above to zero and solving for $\sigma_{\epsilon}^2$ we have
\begin{equation}
 \sigma_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace
\end{equation}

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex

\subsection{Extensions to the framework}
In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption \dean{and show how the support of the connectivity kernel can also be inferred from data}. In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modeled as being isotropic. However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. In addition, natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.

@@

\section{Equivalence to Galerkin's Projection}\label{App:Galerkin}
\dean{To show how equation~\ref{eq:decompRHS} is equivalent to the Galerkin projection, we define the residual between the field and the decomposition as 
\begin{align}\label{eq:BasisFunctionResidual}
	\Xi(\mathbf{x}_t,v_{t+1}&(\mathbf{r})) = v_{t+1}(\mathbf{r}) \nonumber \\
	&- T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
\end{align} 
The Galerkin projection method finds $\mathbf{x}_t$, such that the inner product of the residual with all of the basis functions satisfies
\begin{equation}\label{eq:GalerkinProjection}
	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0,
\end{equation}
where $i=0,1,\hdots,n_x-1,$ and $n_x$ is the number of states and basis functions. If equation~\ref{eq:GalerkinProjection} is satisfied the basis functions are orthogonal to the residual. By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} of the main text. Note, if Galerkin's method was used estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling. The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation. }

@@

\section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}, which provide conditions on distance between the sensors and the field basis functions. The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}. Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. Noise-free observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
\begin{equation}
	y(\mathbf{r}_n)=\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations are described in matrix form by
\parham{\begin{equation}
	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}).
\end{equation}}
The Fourier transform of $\mathbf{y}$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right),
\end{align} 
where $\mathbf{k}$ is an $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}$). It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $n\Delta_y^{-1}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\boldsymbol{\nu}_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter, an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\boldsymbol{\nu}_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$.}

>>>>

\subsection{Extensions to the Framework}
In this study, an assumption was made that the chosen kernel basis functions can exactly represent the actual connectivity kernel. In future work, we plan to relax this assumption \dean{and show how the support of the connectivity kernel can also be inferred from data}. In addition, we have assumed that the neural field is isotropic and homogeneous. It is generally accepted that the intracortical connectivity structure can be accurately modeled as being isotropic. However, the assumption of homogeneity is quite strong as the size of the neural field becomes larger. Future work should focus on developing estimation algorithms where assumptions of homogeneity can be relaxed. In addition, natural extensions of this framework are the inclusion of a post-synaptic response kernel with a finite rise and decay time, and a finite distant-dependant action potential propagation velocity into the parametric neural field equations.

@@

\section{Equivalence to Galerkin's Projection}\label{App:Galerkin}
\dean{To show how equation~\ref{eq:decompRHS} is equivalent to the Galerkin projection, we define the residual between the field and the decomposition as 
\begin{align}\label{eq:BasisFunctionResidual}
	\Xi(\mathbf{x}_t,v_{t+1}&(\mathbf{r})) = v_{t+1}(\mathbf{r}) \nonumber \\
	&- T_s\int_\Omega{f(\boldsymbol{\phi}^{\top}(\mathbf{r}')\mathbf{x}_t )\boldsymbol{\psi}^{\top}(\mathbf{r}-\mathbf{r}') \, d\mathbf{r}'}\boldsymbol{\theta} \nonumber \\
	&+ \xi\boldsymbol{\phi}^{\top}(\mathbf{r})\mathbf{x}_t + \mathbf{e}_t(\mathbf{r}).
\end{align} 
The Galerkin projection finds $\mathbf{x}_t$, such that the inner product of the residual with all of the basis functions satisfies
\begin{equation}\label{eq:GalerkinProjection}
	G_i = \int_{\Omega}\Xi(\mathbf{x}_t,v_{t+1}(\mathbf{r})) \phi_i(\mathbf{r}) d\mathbf{r} = 0,
\end{equation}
where $i=0,1,\hdots,n_x-1,$ and $n_x$ is the number of states and basis functions. If equation~\ref{eq:GalerkinProjection} is satisfied the basis functions are orthogonal to the residual. By substituting equation~\ref{eq:BasisFunctionResidual} into equation~\ref{eq:GalerkinProjection} and rearranging we get equation~\ref{eq:decompRHS} of the main text. Note, if Galerkin's method was used estimate the states, $n_x$ coupled ODEs would need to be solved independently (each $G_i$) to estimate the state vector, which is a standard method in fluid dynamics and economics modeling. The method in this paper takes a different approach by forming the state-space model, allowing for more efficient estimation. }

@@

\section{Derivation of Sampling Theorem}\label{App:SamplingTheorem}
\dean{This appendix provides a derivation for equations~\ref{eq:MinimumSensorDistance} and \ref{eq:BasisFunctionSeparation}, which provide conditions on distance between the sensors and the field basis functions. The derivation is adapted from \citet{Sanner1992} and \citet{Scerri2009}. Consider the cortical sheet defined on the surface $\Omega$ with sensors placed on a regular grid at positions $\mathbf{r}_n$ (where $n=0,...,n_y-1$ indexes the sensors) that are separated by the distance $\Delta_y$. Noise-free observations can be considered samples from a continuous field that is filtered (convolved) with the observation kernel described by
\begin{equation}
	y(\mathbf{r}_n)=\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}),
\end{equation} 
where $v_m(\mathbf{r}) = v_t(\mathbf{r})\ast m(\mathbf{r})$. The observations are described in matrix form by
\parham{\begin{equation}
	\mathbf y=\sum_{n=0}^{n_y-1}\delta(\mathbf r - \mathbf{r}_n ) v_m(\mathbf{r}).
\end{equation}}
The Fourier transform of $\mathbf{y}$ is
\begin{align}
 Y(\boldsymbol{\nu}) &= \frac{1}{\Delta_y^2}\sum_{n=0}^{n_y-1} \delta\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right) \ast V_m(\boldsymbol \nu) \\
	&= \frac{1}{\Delta_y^2}V_m(\boldsymbol\nu) + \frac{1}{\Delta_y^2} \sum_{n=1}^{n_y-1} V_m\left(\boldsymbol{\nu}-\frac{\mathbf{k}_n}{\Delta_y}\right),
\end{align} 
where $\mathbf{k}$ is an $n_y \times 2$ matrix, spatially indexing the sensors (the columns are different spatial dimensions such that $\mathbf{r}_n = \Delta_y \mathbf{k}_n$). It should be clear that $Y(\boldsymbol{\nu})$ contains $V_m(\boldsymbol\nu)$ plus $n_y-1$ copies (aliases) of $V_m(\boldsymbol\nu)$ repeated on the regular lattice, where each copy is centered at $\mathbf{k}_n\Delta_y^{-1}$. Due to the lowpass action of the observation kernel, the filtered dynamic field is band-limited with a cutoff frequency $\boldsymbol\nu_{cy}$. In order for $V_m(\boldsymbol\nu)$ to be disjointed from its aliases, the amount of shift $\Delta_y^{-1}$ must be at least $2\boldsymbol\nu_{cy}$, since each alias has a spectral range of
\begin{equation}
	\boldsymbol\nu = \left[\frac{\mathbf{k}_n}{\Delta_y}-\boldsymbol{\nu}_{cy},\frac{\mathbf{k}_n}{\Delta_y}+\boldsymbol{\nu}_{cy}\right].
\end{equation}
Therefore, to avoid aliasing the distance between observations must satisfy
\begin{equation}\label{eq:SamplingCriteria}
	\frac{1}{\Delta_y} \ge 2\boldsymbol{\nu}_{cy}.
\end{equation}
Since the observation kernel is not an ideal filter, an oversampling parameter should be included to further separate the aliases. Rearranging equation~\ref{eq:SamplingCriteria} and adding the oversampling parameter, $\rho$, gives
\begin{equation}\label{ap:Shannon}
	\Delta_y\le\frac{1}{2\rho\boldsymbol{\nu}_{cy}},
\end{equation}
where $\rho \in \mathbb{R} \ge 1$.}
